Analysis of $\piup$-$\piup$ lattice QCD scattering data

### 2015-02-22 Paper.tex
Add a caption

\begin{figure}[htbp]
    \centering
    \includegraphics[width=\linewidth]{sketches/Zeichnung.pdf}
    \caption{%
        Data flow in the analysis.
    }
    \label{fig:analysis-flow}
\end{figure}

\subsection{Import data}

@@

\subsection{Bootstrap}

@@

\subsection{Correlated fit}

@@

\subsection{Scattering length}

@@

\section{Results}

>>>>

\begin{figure}[htbp]
    \centering
    \includegraphics[width=\linewidth]{sketches/Zeichnung.pdf}
    \caption{%
        Data flow in the analysis. The first is the import of the data, which
        is covered in section~\ref{sec:import}. The two and four point
        functions are combined into pairs for each configuration. The data is
        then folded in half. The bootstrap step is covered in
        section~\ref{sec:bootstrap}. Then a correlated fit is performed, see
        section~\ref{sec:correlated_fit} for details. The second to last step
        is the application of Lüscher's formula, see
        section~\ref{sec:scattering_length}. The results are shown in
        section~\ref{sec:results}.
    }
    \label{fig:analysis-flow}
\end{figure}

\subsection{Import data}
\label{sec:import}

@@

% TODO Folding

\subsection{Bootstrap}
\label{sec:bootstrap}

@@

\subsection{Correlated fit}
\label{sec:correlated_fit}

@@

\subsection{Scattering length}
\label{sec:scattering_length}

@@

\section{Results}
\label{sec:results}
